\refstepcounter{appendixctr}\label{photocreditsappendix}%
\appendix\chapter{Appendix \ref{photocreditsappendix}: Photo Credits}
Except as specifically noted below or in a parenthetical credit in the
caption of a figure, all the illustrations in this book are
under my own copyright, and are copyleft licensed under the same license
as the rest of the book. 

In some cases it's clear from the date that the
figure is public domain, but I don't know the name of the artist or photographer; I would
be grateful to anyone who could help me to give proper credit.
I have assumed that images
that come from U.S. government web pages are copyright-free, since products
of federal agencies fall into the public domain.
When ``PSSC Physics'' is given as a credit, it indicates that the figure
is from the second edition of the textbook entitled Physics, by the
Physical Science Study Committee; these are used according to a blanket
permission given in the later PSSC College Physics edition, which states
on the copyright page that ``The materials taken from the original and second
editions and the Advanced Topics of PSSC PHYSICS included in this text
will be available to all publishers for use in English after December 31, 1970,
and in translations after December 31, 1975.'' 

In a few cases, I have made use of images under the fair use doctrine. However,
I am not a lawyer, and the laws on fair use are vague, so you should not assume
that it's legal for you to use these images. In particular, fair use law may
give you less leeway than it gives me, because I'm using the images for
educational purposes, and giving the book away for free. Likewise, if the
photo credit says ``courtesy of ...,'' that means the copyright owner gave
me permission to use it, but that doesn't mean you have permission to use it.

%\newcommand{\cred}[3]{\noindent\textbf{\pageref{#1}} \emph{#2} #3\par}
\newcommand{\cred}[3]{\textbf{\pageref{#1}} \emph{#2:} #3.\quad}
\newcommand{\credtwo}[4]{\textbf{\pageref{#1},\pageref{#2}} \emph{#3:} #4.\quad}
\newcommand{\credthree}[5]{\textbf{\pageref{#1},\pageref{#2},\pageref{#3}} \emph{#4:} #5.\quad}

\begin{sloppypar}
\noindent
\cred{fig:noether}{Emmy Noether}{I do not know who the photographer was. Based on Noether's apparent age, the portrait
must have been taken around 1900 or 1910, so it is presumably in the public domain}
\cred{fig:singlesymmetries}{Whirlpool galaxy}{N. Scoville et al., NASA and The Hubble Heritage Team (STScI/AURA). Not copyrighted}
\cred{fig:moresymmetries}{Saturn}{French, Cuzzi, Dones, and Lissauer, NASA and The Hubble Heritage Team (STScI/AURA). Not copyrighted}
\cred{fig:startrails}{Star trails}{GFDL licensed, Wikipedia user Manfreeed}
\cred{fig:schmidtonmoon}{Harrison Schmidt on the moon}{NASA Photo ID: AS17-140-2149. Not copyrighted}
\cred{fig:galileo}{Portrait of Galileo Galilei}{Justus Sustermans, 1636}
\cred{fig:io}{Io}{Voyager 1 image, NASA. Not copyrighted}
\cred{fig:astronautshadows}{Astronauts on Mercury and Ganymede}{Uncopyrighted Apollo 11 images, doctored by the author}
\cred{lab-fig-water}{Refraction of water waves}{PSSC Physics}
\cred{fig:telescope}{Telescope}{Line art by the author. Image of the moon from Apollo 13, NASA, not copyrighted}
\cred{fig:poolskater}{Pool skater}{Courtesy of J.D. Rogge, from www.sonic.net/$\sim$shawn}
\cred{fig:lavoisier}{Portrait of Monsieur Lavoisier and His Wife}{Jacques-Louis David, 1788}
\cred{fig:earth}{Earth seen from Apollo 11}{Nasa photo ID AS11-36-5355. Not copyrighted}
\cred{fig:hooverdam}{Hoover Dam}{U.S. Department of the Interior, Bureau of Reclamation, Lower Colorado Region}
\credthree{fig:irface}{fig:irbike}{fig:irball}{Infrared photographs}
{Courtesy of M. Vollmer and K.P. M\"{o}llmann, Univ. Appl. Sciences,
Brandenburg, Germany, www.fh-brandenburg.de/$\sim$piweb/projekte/thermo\_galerie\_eng.html}
\cred{fig:newton}{Isaac Newton}{Portrait by Godfrey Kneller}
\cred{fig:sled}{Rocket sled}{U.S. Air Force, not copyrighted}
\cred{fig:foucault}{Foucault pendulum}{Contemporary}
\cred{fig:galileotrial}{Trial of Galileo}{Cristiano Banti, 1857}
\cred{einstein}{Einstein}{``Professor Einstein's Visit to the United States,'' The Scientific Monthly 12:5 (1921), p. 483, public domain}
\cred{fig:rhic}{Colliding nuclei}{Courtesy of RHIC}
\cred{fig:sunspot}{Sunspot}{Royal Swedish Academy of Sciences. The astronomers' web page at
  http://www.solarphysics.kva.se/NatureNov2002/press\_images\_eng.html states ``All images are free for publication.''}
\cred{fig:millikan}{Millikan}{contemporary}
\cred{fig:doubleslit}{Double-slit diffraction pattern of water waves}{Collage made from PSSC Physics photos}
\end{sloppypar}


